%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Aditya Kumar} & Email : \href{mailto:aditya30394@tamu.edu}{aditya30394@tamu.edu}\\
  Graduate Student & LinkedIn : \href{https://www.linkedin.com/in/aditya30394}{https://www.linkedin.com/in/aditya30394} \\
  \href{http://aditya30394.com/}{Personal Web Page} & Mobile : +1-9793087076 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Texas A\&M University (College Station)}{Texas, USA}
      {Master of Science in Computer Science;  \textbf{GPA: Not Available }}{Fall 2018 -- Spring 2020}
    \resumeSubheading
      {National Institute of Technology Calicut (NIT Calicut)}{Kerala, India}
      {Bachelor of Technology in Computer Science and Engineering;  \textbf{CGPA:  9.37/10.0}}{July 2012 -- May 2016}
    \resumeSubheading
      {12th standard All India Senior Secondary Certificate Examination (AISSCE)}{New Delhi, India}
      {Kendriya Vidyalaya, Central Board of Secondary Education \textbf{(CBSE)} \textbf{Percentage : 94.6\%}}{2011}
    \resumeSubheading
      {10th standard All India Senior Secondary Examination (AISSE)}{Patna, India}
      {Kendriya Vidyalaya, Central Board of Secondary Education \textbf{(CBSE)} \textbf{Percentage : 91.0\%}}{2009}  
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sandvine Technologies}{Bengaluru, Karnataka, India}
      {Software Development Engineer}{June 2016 - Present}
      \resumeItemListStart
        \resumeItem{Automatic Calibration in Quality Guard}
          {Quality Guard is a fuzzy control system which generates the optimal shaping rate to improve the Quality of Experience (QoE) during network congestion. The output rate is then used as the input to shape the subscriber's traffic. Currently, working on automatically calibrating the values of few parameters based on locations so that customers won't need to fine tune any of Quality Guard's parameter.}  
        \resumeItem{Distributed Dynamic Shaping using REST API}
          {Extended the capability of level distributed traffic shapers by allowing their shaping rates to be set dynamically using REST API and thereby preventing unnecessary system reloads.}  
        \resumeItem{Fraud Detection}
          {Worked on anomaly detection algorithms to detect masquerading traffic which exploits the zero-rating capability of Sandvine.}
        \resumeItem{Application fingerprinting}
          {Developed advanced behavioural classification technique improving the identification of applications which heavily rely on third-party services.}
        \resumeItem{Sandvine Genie (Hackathon Winner)}
          {The voice-based surveillance system is capable of report generation based on multiple parameters and detecting unusual traffic trend based on the probe results from USA, West Indies, etc.}  
        \resumeItem{Web and Streaming separation}
          {Identification mechanism to separate the streaming part from the usual browsing traffic on popular websites like nytimes.com, abc.com, foxnews.com, etc. One of the use cases was to block the streaming traffic to save bandwidth in the network. }
        \resumeItem{Game, App and Fraud Crawlers}
          {Java-based crawlers to help Sandvine stay on the top of internet changes. These detect trending games, app updates and helps prevent abuse of zero-rating capabilities. }
        
      \resumeItemListEnd

    \resumeSubheading
      {InApp Inc.}{Trivandrum, India}
      {Software Development Intern}{May 2015 - July 2015}
      \resumeItemListStart
        \resumeItem{Recruitment Application}
          {Designed and built a fully featured application giving solutions for every step involved in the hiring process ranging from scheduling interviews to giving out appointment letter. MVC architecture was used with PHP as back-end.  }
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Kernel based simulation study of RSDM-A}
      {The project aimed at improving the security of virtual machines in cloud computing environment. The area of focus was rollback related security issues.}
    \resumeSubItem{Research collaborator}
      {Laravel based \href{https://ccrg.cse.nitc.ac.in/}{secure content} sharing system for various research activities going on in the CSE Department.}
    \resumeSubItem{Android application for Tathva}
      {Developed an android application for Tathva - annual techno-management festival, organized by the National Institute of Technology Calicut}
    \resumeSubItem{Sentiment analysis (ML)}
      {A natural language processing (NLP) project to classify reviews as positive or negative using \href{https://github.com/Anand-M-P/NLP-Project}{Multinomial Naive Bayes Classifier} in Python}.
    \resumeSubItem{eXperimental Operating System (XOS)}
      {\href{http://xosnitc.github.io/}{Toy OS} designed to run on the XSM (eXperimental String Machine) architecture with features like multiprogramming, virtual memory, and system calls.}
    \resumeSubItem{Simple Integer Language Compiler (SILC)}
      {Compiler developed for \href{http://silcnitc.github.io/}{SIL (Simple Integer Language)} in C using tools Lex and Yacc with support for basic and user-defined data types, functions, conditional and iterative statements.}
    \resumeSubItem{Predict if a car purchased at auction is good (Data Mining)}
      {The dataset from \href{https://www.kaggle.com/c/DontGetKicked}{Kaggle} was cleaned using bayesian cleaning and mean median max methods. Then, classification models namely Random forest (prune based) and fuzzy rule learner were implemented and compared for accuracy(\textbf{ 86.4\% and 83.1\% respectively}). }  
  \resumeSubHeadingListEnd


\section{Publications}
  \resumeSubHeadingListStart
    \resumeSubItem{Multikernel Simulation: A new approach to study rollback sensitive memory architecture}
    {The \href{https://ieeexplore.ieee.org/document/8181523/}{paper} was published in \textbf{\textit{2017 IEEE 3\tr{rd} International Conference on Collaboration and Internet Computing (CIC), San Jose, California}}.}
    
  \resumeSubHeadingListEnd
%

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
    {C++, Java, MySQL, C, Python}
    \resumeSubItem{Web Technologies}
    {MySQL, HTML, JavaScript, jQuery, PHP, CSS}
  \resumeSubHeadingListEnd


%-------------------------------------

\iffalse
%--------AREAS OF INTEREST------------
\section{Areas of Interest}
  \resumeSubHeadingListStart
    \resumeSubItem{Areas}
    {Machine learning and its application, particularly using unsupervised learning;
     Natural Language Processing (NLP); Advanced data structures and algorithms; Advanced database management systems}
    \resumeSubItem{Relevant coursework}
    {Data mining in 6th semester; Natural Language Processing (NLP) in 8th semester;  Design and analysis of algorithms in 5th semester; Advanced database management systems in 8th Semester;}
  \resumeSubHeadingListEnd

%-------------------------------------
\fi

%--------OTHER-----------
\section{Other}
  \resumeSubHeadingListStart
    \resumeSubItem{Certificate}{\textbf{Machine Learning} by Stanford University on Coursera. Certificate earned on October 14, 2017}   
    \iffalse
    \resumeSubItem{Hackathon 2017 winner}
    {Won the popular choice award for the Hackathon project - Sandvine Genie}
    \fi
    \resumeSubItem{Merit certificate in Mathematics and Chemistry}
    {For reasons of outstanding performance and for being among the top 0.1 percent of successful candidates of AISSCE 2011}
    
  \resumeSubHeadingListEnd

\end{document}
