%-------------------------
% Resume in Latex
% Author : Aditya Kumar
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{lastpage}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
%\fancyfoot[R]{\thepage}
%\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeEduHeading}[4]{
    \vspace{-1pt}
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
}

\newcommand{\resumeExpHeading}[4]{
    \vspace{-1pt}
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}{, #2} & #4 \\
      \textit{\small#3} &  \\
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\huge Aditya Kumar} & Email : \href{mailto:aditya30394@tamu.edu}{aditya30394@tamu.edu}\\
  4302 College Main Street Apt 226&  \href{mailto:aditya30394@gmail.com}{aditya30394@gmail.com} \\
  Bryan, TX 77801 & LinkedIn : \href{https://www.linkedin.com/in/aditya30394}{https://www.linkedin.com/in/aditya30394} \\
  Phone : 979-308-7076 & GitHub : \href{https://github.com/aditya30394}{https://github.com/aditya30394} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
    \resumeEduHeading
      {Texas A\&M University, College Station, Texas}{August 2018 -- May 2020}
      {Master of Science in Computer Science;  \textbf{GPA: 1st Semester }}{}
    \resumeEduHeading
      {National Institute of Technology Calicut, India} {July 2012 -- May 2016}
      {Bachelor of Technology in Computer Science and Engineering;  \textbf{GPA:  9.37/10.0}}{}
\iffalse
    \resumeEduHeading
      {12th standard All India Senior Secondary Certificate Examination (AISSCE)}{New Delhi, India}
      {Kendriya Vidyalaya, Central Board of Secondary Education \textbf{(CBSE)} \textbf{Percentage : 94.6\%}}{2011}
    \resumeEduHeading
      {10th standard All India Senior Secondary Examination (AISSE)}{Patna, India}
      {Kendriya Vidyalaya, Central Board of Secondary Education \textbf{(CBSE)} \textbf{Percentage : 91.0\%}}{2009}
\fi      
  
\vspace{-10pt}

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
    {C++ (Proficient), Java (Prior Experience), MySQL, C, Python, Shell Scripting}
    \resumeSubItem{Web Technologies}
    {HTML, JavaScript, jQuery, PHP, CSS}
  \resumeSubHeadingListEnd
%-------------------------------------
%-----------EXPERIENCE-----------------
\section{Experience}

    \resumeExpHeading
      {Sandvine Technologies}{Bengaluru, Karnataka, India}
      {Software Engineer (45-50 hours/week)}{June 2016 - July 2018}
      \resumeSubHeadingListStart
        \resumeSubItem{Automatic Calibration in Quality Guard}
          {Quality Guard is a fuzzy control system which generates the optimal shaping rate to improve the Quality of Experience (QoE). I devised a system to automatically calibrate the values of few parameters to eliminate manual calibration in a large cluster - consisting of more than 1000 locations. (C++)}  
        \resumeSubItem{Distributed Dynamic Shaping}
          {Upgraded the capability of level distributed traffic shapers by allowing their shaping rates to be set dynamically using REST API and thereby preventing unnecessary system reloads. (C++)}  
        \resumeSubItem{Application Fingerprinting}
          {Developed advanced behavioural classification technique improving the identification of applications which heavily rely on third-party services. (C++)}
        \resumeSubItem{Sandvine Genie (Hackathon Winner)}
          {Developed voice-based surveillance system capable of report generation and detecting unusual traffic trend based on the probe results from USA, West Indies, etc. (Java, PHP, api.ai)}
        \resumeSubItem{Fraud Detection (Proof of Concept)}
          {Investigated on anomaly detection algorithms to detect masquerading traffic which exploits the zero-rating capability of Sandvine. (Python, Shell scripting)}
        \resumeSubItem{Web and Streaming Separation}
          {Designed identification mechanism to separate the streaming part from the usual browsing traffic on popular websites like nytimes.com, abc.com, foxnews.com, etc. (C++)}
        \resumeSubItem{Reduced System Reloads by 3 Seconds}
          {Improved system reloads time by removing unnecessary file-based configuration reads and using efficient data structures like maps and sets. (C++)}
        \iffalse  
        \resumeItem{Network Forensics using Machine Learning}
          {Project to detect Malware inside TCP packet based on their
          anomalous characteristics. The TCP header fields are used as datasets to implement the machine learning model.}
        \fi  
        \resumeSubItem{App and Game Crawlers}
          {Java based crawlers to detect trending games and app updates. (Java, Shell scripting)}
        
      \resumeSubHeadingListEnd
\vspace{7pt}
    \resumeExpHeading
      {InApp Inc.}{Trivandrum, India}
      {Software Development Intern (40-45 hours/week)}{May 2015 - July 2015}
      \resumeSubHeadingListStart
        \resumeSubItem{Recruitment Application}
          {Engineered a web application giving solutions for every step involved in the hiring process ranging from scheduling interviews to giving out the appointment letter. (MVC architecture + PHP)  }
      \resumeSubHeadingListEnd
  

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Kernel based simulation study of RSDM-A}
      {Project for preventing roll back attacks in virtual environment which is the back bone of cloud computing. A research paper was published for the same in \textbf{IEEE ISCBD 2107} conference.}
    \resumeSubItem{Research collaborator}
      {Laravel based \href{https://ccrg.cse.nitc.ac.in/}{content sharing system} for various research activities in the CSE Department.}
    \resumeSubItem{Sentiment analysis (ML)}
      {A natural language processing (NLP) project to classify reviews as positive or negative using \href{https://github.com/Anand-M-P/NLP-Project}{Multinomial Naive Bayes Classifier} in Python}.
    \resumeSubItem{eXperimental Operating System (XOS)}
      {\href{http://xosnitc.github.io/}{Toy OS} designed to be run on the XSM (eXperimental String Machine) architecture with features like multiprogramming, virtual memory, and system calls.}
    \resumeSubItem{Simple Integer Language Compiler (SILC)}
      {Compiler developed for \href{http://silcnitc.github.io/}{SIL (Simple Integer Language)} in C using tools Lex and Yacc with support for basic and user defined data types, functions, conditional and iterative statements.}
    \resumeSubItem{Predict if a car purchased at auction is good (Data Mining)}
      {The dataset from \href{https://www.kaggle.com/c/DontGetKicked}{Kaggle} was cleaned using bayesian cleaning and mean median max methods. Then, classification models namely Random forest (prune based) and fuzzy rule learner were implemented and compared for accuracy(\textbf{ 86.4\% and 83.1\% respectively}). }  
  \resumeSubHeadingListEnd

%
\iffalse
%--------PUBLICATIONS------------------

\section{Publications}
  \resumeSubHeadingListStart
    \resumeSubItem{Multikernel Simulation: A new approach to study rollback sensitive memory architecture}
    {The \href{https://ieeexplore.ieee.org/document/8181523/}{paper} was published in \textbf{\textit{2017 IEEE 3\tr{rd} International Conference on Collaboration and Internet Computing (CIC), San Jose, California}}.}
    
  \resumeSubHeadingListEnd
%-------------------------------------

%--------OTHER-----------
\section{Other}
  \resumeSubHeadingListStart
    \resumeSubItem{Hackathon 2017 winner}
    {Won the popular choice award for the Hackathon project - Sandvine Genie}
    \resumeSubItem{Certificate}{\textbf{Machine Learning} by Stanford University on Coursera. Certificate earned on October 14, 2017}
    \resumeSubItem{Merit certificate in Mathematics and Chemistry}
    {For reasons of outstanding performance and for being among the top 0.1 percent of successful candidates of AISSCE 2011}
  \resumeSubHeadingListEnd
%-------------------------------------------

\fi
%--------WORK AUTHORIZATION-----------
\section{Work Authorization}
  \resumeSubHeadingListStart
    \resumeSubItem{Eligible to intern in the US for 12 months under CPT}{}
  \resumeSubHeadingListEnd
%-------------------------------------------

\end{document}
