%-------------------------
% Resume in Latex
% Author : Aditya Kumar
% License : MIT
%------------------------

\documentclass[11pt]{article}
\usepackage[left=2cm, right=1cm, top=2cm]{geometry}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{lastpage}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\usepackage{titlesec}
\titleformat*{\section}{\LARGE\bfseries}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
%\fancyfoot[R]{\thepage}
%\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemSmall}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeEduHeading}[4]{
    \vspace{-1pt}
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
}

\newcommand{\resumeExpHeading}[5]{
    \vspace{-1pt}
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\large#1}{#2} & #5 \\
      \textbf{#3}\text{#4} &  \\
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemSmall}[2]{\resumeItemSmall{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand{\normalListItem}[1]{\item{#1}\vspace{-6pt}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\huge Aditya Kumar} & Email : \href{mailto:aditya30394@tamu.edu}{aditya30394@tamu.edu}\\
  4302 College Main Street Apt 226&  \href{mailto:aditya30394@gmail.com}{aditya30394@gmail.com} \\
  Bryan, TX 77801 & LinkedIn : \href{https://www.linkedin.com/in/aditya30394}{https://www.linkedin.com/in/aditya30394} \\
  Phone : 979-308-7076 & GitHub : \href{https://github.com/aditya30394}{https://github.com/aditya30394} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{EDUCATION}
    \resumeEduHeading
      {Texas A\&M University, College Station, Texas}{August 2018 -- May 2020}
      {Master of Science in Computer Science;  \textbf{GPA: 4.0/4.0 }}{}
    \resumeEduHeading
      {National Institute of Technology Calicut, India} {July 2012 -- May 2016}
      {Bachelor of Technology in Computer Science and Engineering;  \textbf{GPA:  9.37/10.0}}{}
\vspace{-10pt}

%--------PROGRAMMING SKILLS------------
\section{PROGRAMMING SKILLS}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
    {C++ (Proficient), Java (Prior Experience), C, Python, MySQL, Shell Scripting}
    \resumeSubItem{Web Technologies}
    {HTML, JavaScript, jQuery, PHP, CSS}
    \resumeSubItem{Tools}
    {Git, GitHub, GNU Debugger, Lex, Yacc, Laravel, Rational ClearCase}
  \resumeSubHeadingListEnd
%-------------------------------------
%-----------EXPERIENCE-----------------
\section{EXPERIENCE}

    \resumeExpHeading
      {Sandvine Technologies}{, Bangalore, India}
      {Software Engineer} {}{June 2016 - July 2018}
      \resumeSubHeadingListStart
        \normalListItem
        {Automated calibration of parameters in fuzzy control system by developing service using C++ capable of monitoring network traffic over 100,000 locations.}  
        \normalListItem
          {Designed REST APIs for traffic shapers in C++ enabling internet providers to enforce dynamic policies without any maintenance window. This saves 9 hours (average) of maintenance time per month.}  
        \normalListItem
          {Developed hash map and timers based classification mechanism in C++ improving identification of applications that rely on third-party services by 90\% (on average).}
        \normalListItem
          {Improved system reloads time by 10\% using efficient data structures like maps and sets, thereby removing file-based configuration reads. (C++)}
      \resumeSubHeadingListEnd
\vspace{7pt}
    \resumeExpHeading
      {InApp Inc.}{, Trivandrum, India}
      {Software Development Intern} {}{May 2015 - July 2015}
      \resumeSubHeadingListStart
        \resumeSubItem{Recruitment Application}
          {Led a 3-member team and engineered web application for the company in PHP using MVC architecture capable of handling every step involved in the hiring process.}
      \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------------
\section{PROJECTS}
  \resumeSubHeadingListStart
    \resumeSubItem{Sandvine Genie (Hackathon Winner)}
          {Developed voice controlled system using PHP and \href{https://dialogflow.com/}{``api.ai''} capable of report generation and detecting unusual traffic trend based on probe results from USA, West Indies, etc.}
    \resumeSubItem{Kernel based simulation study of RSDM-A}
      {Modified memory management unit of Xen hypervisor (written in C) by implementing an in-memory table to prevent rollback attacks. A research paper was published for the same in \href{https://ieeexplore.ieee.org/document/8181523/}{IEEE ISCBD 2107} conference.}
    \resumeSubItem{eXperimental Operating System (XOS)}
      {Designed \href{http://xosnitc.github.io/}{OS} and implemented important interrupt routines, scheduling algorithm and system calls.}
    \resumeSubItem{Simple Integer Language Compiler (SILC)}
          {Developed compiler for \href{http://silcnitc.github.io/}{``Simple Integer Language''} in C using Lex and Yacc supporting user defined data types, functions, conditional and iterative statements.}
    \resumeSubHeadingListEnd

%
%-----------LEADERSHIP-----------------
\section{LEADERSHIP}

    \resumeExpHeading
      {Computer Science Graduate Student Association (CSEGSA)}{}
      {Treasurer}{}{August 2018 -- Present}
      \resumeSubHeadingListStart
        \normalListItem
          \small{Responsible for overseeing and presenting budgets, accounts and financial statements of the association}
        \resumeSubHeadingListEnd

%--------WORK AUTHORIZATION-----------
\section{WORK AUTHORIZATION}
  \resumeSubHeadingListStart
    \resumeSubItemSmall{Eligible to intern in the US for 12 months under CPT}{}
  \resumeSubHeadingListEnd
%-------------------------------------------

\end{document}
